### 2015-11-13 ch02-qlogms/excitation-design.tex
Finished table on MS excitation

  \begin{definition}
  The effective frequency ratio $\alpha_k$ of a frequency grid is
  \begin{equation}
    \alpha_k \isdef  \frac{f_k}{f_k-1}
    \text{.}
  \end{equation}
  \end{definition}

  \begin{remark}
  For the implementation of a quasi-logarithmic frequency grid,  the approximate equality  \label{eq:qlogGrid} does not define the grid unambiguously.
  The quasi-logarithmic grids constructed in this chapter are constructed using the relationship
  \begin{equation}
    f_k = \alpha_k f_{k-1} 
    \text{ with } 
      \alpha_k \isdef 
          \round{   \frac{\alpha f_{k-1}}{\Delta f}}    
           \frac{\Delta f}{f_{k-1}}
      \approx \alpha 
      \emspace 
          \forall k \in \set{1,\ldots,F}
     \text{.}
     \label{eq:excitation:qlog:round}
  \end{equation}
  In the equation above, $\round{\placeholder}$ denotes rounding towards the nearest integer as in the \MATLAB function \code{round}.
  This satisfies the approximate definition.
  \end{remark}

  \begin{remark}
  The use of different rounding strategies in \eqref{eq:excitation:qlog:round}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
  By denoting $\alpha_k^{\placeholder}$ as the effective frequency ratio for a rounding strategy $\placeholder$  in that equation, one can trivially see that the following relationships hold:
  \begin{equation}
  \alpha_k^{\floor{}} \leq \alpha \leq  \alpha_k^{\ceil{}}
  \qquad \text{and} \qquad
  \alpha_k^{\floor{}} \leq \alpha_k^{\round{}} \leq  \alpha_k^{\ceil{}}
  \qquad
  \forall k \in \set{1,\ldots,F}
  \text{.}
  \end{equation}
  \end{remark}

@@

  \begin{table}
  \centering
   \caption{Summary of the different frequency grids.}
    \begin{tabular}{lccc} 
    Grid & Linear & Logarithmic & Quasi-logarithmic \\

    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Parameters & $f_0, \Delta f$ & $f_0, \alpha$ & $f_0, \Delta f, \alpha$ \\
    $f_{k+1} \isdef$ & $f_{k} + \Delta f$ & $f_{k} \cdot \alpha$ & \ldots \\

    \end{tabular}
    \TODO{afmaken, booktabs}
  \end{table}

>>>>

  \begin{definition}
  The effective frequency ratio $\alpha_k$ of a frequency grid is
  \begin{equation}
    \alpha_k \isdef  \frac{f_k}{f_{k-1}}
    \text{.}
  \end{equation}
  \end{definition}

  \begin{definition}
  For the implementation of a quasi-logarithmic frequency grid,  the approximate equality \eqref{eq:qlogGrid} does not define the grid unambiguously.
  The quasi-logarithmic grids depicted in this chapter are constructed using the relationship
  \begin{align}
       \label{eq:excitation:qlog:gridDef}
    f_k & = \alpha_k(N_k) f_{k-1}  
        \quad
            \forall k \in \set{1,\ldots,F}
\end{align}
with
\begin{align}
     \label{eq:excitation:qlog:roundAlpha}
      \alpha_k(N_k) & \isdef 
          \round{   \frac{\alpha^{N_k} f_{k-1}}{\Delta f}}    
           \frac{\Delta f}{f_{k-1}}
      \approx \alpha \text{, and}\\
         \label{eq:excitation:qlog:alphaPowerDef}
          N_k & \isdef 
            \min 
            \set{n | n \in \NaturalNumbers, \alpha_k(n) > 1}
     \text{.}
  \end{align}
  \end{definition}
  In the equation above, $\round{\placeholder}$ denotes rounding towards the nearest integer according to the \IEEEfloat standards and as implemented in the \MATLAB function \code{round}.
  This satisfies the approximate definition.

  \begin{remark}
  The use of different rounding strategies in \eqref{eq:excitation:qlog:roundAlpha}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
  By denoting $\alpha_k^{\placeholder}$ as the effective frequency ratio for a rounding strategy $\placeholder$  in that equation, one can trivially see that the following relationships hold:
  \begin{equation}
  \alpha_k^{\floor{}} \leq \alpha \leq  \alpha_k^{\ceil{}}
  \qquad \text{and} \qquad
  \alpha_k^{\floor{}} \leq \alpha_k^{\round{}} \leq  \alpha_k^{\ceil{}}
  \qquad
  \forall k \in \set{1,\ldots,F}
  \text{.}
  \end{equation}
  \end{remark}

@@

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
    Grid & Linear & Logarithmic & Quasi-logarithmic \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$ 
       & $\round{\frac{\alpha f_k}{\Delta f}} \Delta f$\\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & \ldots\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}

    \TODO{afmaken}
  \end{table}
